Once we have chosen the resolutions $(N_\theta,N_\zeta,N_\xi)$ for each case, we need to verify that these selections indeed provide sufficiently accurate calculations of all the monoenergetic coefficients in the interval $\hat{\nu}\in[10^{-5},300]$ $\text{m}^{-1} $. In all cases, {\MONKES} calculations of the $\widehat{D}_{11}$ and $\widehat{D}_{31}$ coefficients will be benchmarked against converged calculations from {\DKES} (see \ref{sec:Appendix_DKES_Bounds}) and from \texttt{SFINCS}\footnote{\texttt{SFINCS} calculations are converged up to 3\% in the three independent variables.}. The parallel conductivity coefficient will be benchmarked only against {\DKES}. The benchmarking of the coefficient $\widehat{D}_{11}$ for the six different cases is shown in figure \ref{fig:D11_Benchmark}. The result of the benchmark of the bootstrap current coefficient $\widehat{D}_{31}$ is shown in figure \ref{fig:D31_Benchmark}. Finally, the parallel conductivity coefficient $\widehat{D}_{33}$ is benchmarked in figure \ref{fig:D33_Benchmark}. Due to the weak effect of the radial electric field in the $\widehat{D}_{33}$ coefficient, the symbols for this plot have been changed. In all cases, the agreement between {\MONKES}, {\DKES} and \texttt{SFINCS} is almost perfect. Thus, we conclude that {\MONKES} calculations of the monoenergetic coefficients are not only fast, but also accurate. Additionally, we can evaluate the level of optimization of the three configurations considered by inspecting these plots. In figures \ref{subfig:D11_Benchmark_W7X_EIM} and \ref{subfig:D11_Benchmark_W7X_KJM} is shown that the W7X-EIM configuration has smaller radial transport coefficient than the W7X-KJM configuration. Figures \ref{subfig:D31_Benchmark_W7X_EIM} and \ref{subfig:D31_Benchmark_W7X_KJM} show that the smaller radial transport of the W7X-EIM  configuration comes at the expense of having larger bootstrap current coefficient. As shown in figures \ref{subfig:D11_Benchmark_CIEMAT_QI} and \ref{subfig:D31_Benchmark_CIEMAT_QI}, the optimized stellarator CIEMAT-QI manages to achieve levels of radial transport similar or smaller than the W7X-EIM configuration and a bootstrap current coefficient as low as the W7X-KJM configuration.
%


\input{sections/D11_Benchmark.tex}
\input{sections/D31_Benchmark.tex}
\input{sections/D33_Benchmark.tex}

%\FloatBarrier